---
title: "Weight of Fish"
author: "Desmond Koutso"
date: "`SUMMER 2022`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

From this graph, I see that the 2 predictions of weights are length3 and height.    

## Perch
```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

### Best Two regressor model

From the graph, the best two regressor model for Perch is lenght3 and Height.    

## Pike


```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Pike)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
### Best Models

### Best Two regressor model

From the graph, the best two regressor model for Pike is length2 and length3.    

## Roach

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Roach)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

### Best Two regressor model

From the graph, the best two regressor model is length2 and length3.  

## Final Summary Statements

When predicting fish weight, it was seen from the table that the 2 predictions were weight and length3.  
Also, when analyzing the 2 best regressor models for Pearch, it came out to be length3 and weight.  
For Pike, the 2 best regressor model is length2 and length3.  
Lastly, for Roach, the 2 best regressor models is length2 and length3. 

